The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-23 paper/ms.tex
update paper

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  The CDIPS project is processing the TESS
  full-frame images and making light curves of stars that could be
  members of stellar associations, moving groups, or open clusters.
  %
  Our eventual hope is to discover giant transiting planets with known
  ages, and probe the exoplanet size and separation distributions for
  planets younger than 1 Gyr.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties in agreement with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the additional spectroscopic, photometric,
  and imaging observations that are needed to verify that these
  candidates are in fact planets.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \url{archive.stsci.edu/prepds/cdips}.
\end{abstract}

@@

%\begin{figure*}[t]
%	\begin{center}
%		\leavevmode
%		\includegraphics[width=0.7\textwidth]{cluster_positions.pdf}
%	\end{center}
%	\vspace{-0.5cm}
%	\caption{
%    {\bf TESS looks at many clusters.} Placeholder skymap.
%		\label{fig:clustermap}
%	}
%\end{figure*}

\begin{figure*}[!ht]
    \gridline{
      \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
      \fig{cam1_cluster_field_star_positions.png}{0.49\textwidth}{}
    }
    %\begin{center}
    %    \leavevmode
    %    \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
    %\end{center}
    \vspace{-0.5cm}
    \caption{
        {\it Left}. Celestial positions of light curves from Sectors 6 and 7.
        {\it Right}. Celestial positions of light curves from Sector 6, Camera 1.
        \label{fig:lcradecsector6}
    }
\end{figure*}

% \begin{figure}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.49\textwidth]{cam1_cluster_field_star_positions.png}
% 	\end{center}
% 	\vspace{-0.5cm}
% 	\caption{
%     {\bf Celestial positions of light curves from Sector 6, Camera 1.}
% 		\label{fig:lcradec}
% 	}
% \end{figure}

@@

However, a homogeneous membership calculation for every known
cluster is outside our scope.  So too is a homogeneous search for
young stars across the galaxy.
Instead, we opt to collect
and concatenate appropriate catalogs from across the literature.  
We then use the resulting meta-catalog to identify our target stars within the 
TESS images.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.}  The selected stars are eiher candidate
    members of clusters, or else have other youth indicators. We only consider stars
    with $G_{\rm Rp} < 16$.
	\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\caption{
		{\it Top.} Cross-match statistics from \cite{Kharchenko_et_al_2013} {\it 
			vs.} Gaia-DR2.
		{\it Bottom.} Ditto, for \cite{dias_proper_2014} {\it vs.} Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{cdf_T_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Cumulative distribution of TESS-band magnitudes for CDIPS
    light curves.}
		\label{fig:cdf_T_mag}
	}
\end{figure}

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
    {\it Top.} HR diagram of CDIPS stars with light curves in this
    data release.  {\it Bottom.} HR diagram of close CDIPS stars with
    light curves. The wedge separating the pre-MS sample from the MS
    stars was discussed by \citet{zari_3d_2018}, who introduced it in
    order to avoid contamination by photometric binaries.
	}
	\label{fig:hrd}
\end{figure}

\begin{figure}[!ht]
	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
	\caption{
    {\it Top.} Proper motions of CDIPS stars with light curves in this
    data release.  {\it Bottom.} Proper motions of close CDIPS stars
    with light curves. A few additional clusters are visible.
	}
	\label{fig:propermotions}
\end{figure}

Describe
Figure~\ref{fig:cdf_T_mag}
Figure~\ref{fig:hrd}
Figure~\ref{fig:propermotions}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} 
  Black points correspond to the minimum RMS across the available three
  aperture sizes.  
  The model (orange and gray lines) uses the optimal aperture sizes reported 
  by \citet{Sullivan_et_al_2015}, and the effective area from 
  \citet{vanderspek_2018}.
  The noise from unresolved background stars (dotted gray line) is a function 
  of galactic latitude, and dominates over zodiacal light and read noise
  for faint stars near the galactic plane; the line shown assumes a
  sight-line towards the center of Sector 6, Camera 1 (further details
  are in \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\begin{figure}[!ht]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

>>>>

\newcommand{\stscilink} {\url{archive.stsci.edu/prepds/cdips}}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) has begun to
  photometrically monitor almost every star cluster in
  the solar neighborhood.
  % Aims
  The CDIPS project is processing the TESS
  full-frame images and making light curves of stars that could be
  members of stellar associations, moving groups, or open clusters.
  %
  Our eventual hope is to discover giant transiting planets with known
  ages, and probe the exoplanet size and separation distributions for
  planets younger than 1 Gyr.
  %
  In this study, we made \numberlcs light curves of candidate young
  stars in \numberclusters clusters.
  Each light curve represents between 20 and 25 days of observations
  of a star brighter than $G_{Rp}=16$, sampled at 30 minute cadence.
  % Methods
  We describe in detail the image subtraction and time-series analysis 
  techniques we used to create the light curves, which
  have noise properties in agreement with theoretical expectations.
  % Results
  We then highlight the \numberpcs planet candidates we identified in
  an initial search, describe the vetting procedures that they have
  survived, and emphasize the additional spectroscopic, photometric,
  and imaging observations that are needed to verify that these
  candidates are in fact planets.
  %
  We also comment on the possible use of the light curve sample for
  studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves and vetting reports are available at
  \stscilink.
\end{abstract}

@@

@@

How
ever, a homogeneous membership calculation for every known
cluster is outside our scope.  So too is a homogeneous search for
young stars across the galaxy.
Instead, we opt to collect
and concatenate appropriate catalogs from across the literature.  
We then use the resulting meta-catalog to identify our target stars within the 
TESS images.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.}  The selected stars are
    either candidate members of clusters, or else have other youth
    indicators (see \S~\ref{sec:starselection}). We only consider
    stars with $G_{\rm Rp} < 16$.
	\label{fig:cdips_targets}
	}
\end{figure}

\begin{figure*}[!ht]
	\gridline{\fig{mwscmatchstats.png}{0.95\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{dias14matchstats.png}{0.95\textwidth}{}}
	\caption{
    {\it Top.} Cross-match statistics from
    \cite{Kharchenko_et_al_2013} cluster members to Gaia-DR2. A
    histogram of the distances between matched stars is on the left; a
    histogram of the difference between the true $G$-band magnitude
    and that predicted from 2MASS photometry in the middle; a scatter
    plot of the same magnitude difference as a function of $G$-band
    magnitude is on the right.
    {\it Bottom.} Same, but cross-matching \cite{dias_proper_2014}
    cluster members to Gaia-DR2.
	}
	\label{fig:xmatch_info}
\end{figure*}

@@

\begin{figure}[!t]
	%\gridline{
	%  \fig{cluster_field_star_positions.png}{0.49\textwidth}{}
	%  \fig{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}{0.49\textwidth}{}
	%}
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Celestial positions of light curves from Sectors 6
			and 7.}  Black: $G_{\rm Rp}<13$ field stars.  Blue: $G_{\rm
			Rp}<16$ target stars.
		\label{fig:lcradec}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{sector6_cam[1]_ccd[1-2-3-4]cluster_field_star_positions.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf  Zoom of Sector 6, Camera 1 from Figure~\ref{fig:lcradec}.}
		\label{fig:lcradeczoom}
	}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{cdf_T_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Cumulative number of CDIPS light curves a function of TESS
    $T$-band magnitude.}  Light curves were made for the subset of
    stars shown in Figure~\ref{fig:cdips_targets} that were observed
    in Sectors 6 or 7.
		\label{fig:cdf_T_mag}
	}
\end{figure}

\begin{figure}[!ht]
	\gridline{\fig{hrd_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{hrd_scat_close_subset.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} HR diagram of CDIPS stars on silicon in this
    data release.  {\it Bottom.} HR diagram of close CDIPS stars on
    silicon. The wedge separating the pre-MS sample from the MS
    stars was discussed by \citet{zari_3d_2018}, who introduced it in
    order to avoid contamination by photometric binaries.
	}
	\label{fig:hrd}
\end{figure}

\begin{figure}[!t]
	\gridline{\fig{pm_scat_all_CDIPS_LCs.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{pm_scat_close_subset.png}{0.45\textwidth}{}}
	\vspace{-0.8cm}
	\caption{
    {\it Top.} Proper motions of CDIPS stars on silicon in this
    data release.  Many of the stars in the central ``blob'' are possible
    field-contaminants.
    {\it Bottom.} Proper motions of close CDIPS stars
    on silicon.
	}
	\label{fig:propermotions}
\end{figure}

The on-sky locations of the light curves from Sectors 6 and 7
are shown in Figure~\ref{fig:lcradec}.
Black stars are the field stars for which we performed photometry,
but only to calibrate the cluster star sample.
The blue stars are the \numberlcs stars with light curves available
from \stscilink.
Most of the target stars are quite close to the galactic plane.
Gaps between CCD chips are also visible.

A zoom-in of Figure~\ref{fig:lcradec} is shown in Figure~\ref{fig:lcradeczoom}
for the Camera 1, Sector 6 field. The effects of galactic-latitude
dependent extinction are visible through the decreasing density of black
points towards the right of the image.
The highly clumped nature of the target stars is also apparent.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of
TESS $T$-band magnitudes for the target stars.
Though most of the targets are faint, $\approx3\times10^4$ are
brighter than $T=13$, and so are more promising targets for any
detailed follow-up observtions.

An HR diagram for the entire sample of stars on silicon
is shown in Figure~\ref{fig:hrd} (top).
The sub-sample of stars with
measured positive parallaxes and naive distances less than
$1\,{\rm kpc}$ is also shown (bottom).
About one-third of the stars are in this latter sample.
The close stars are predominantly on the main-sequence, or the pre-main-sequence.
A relatively large fraction of these come from \citet{zari_3d_2018},
and are either on the PMS or upper main-sequence.
The latter set of OBA dwarf stars, while ``younger'' than the typical
field dwarf, are likely the least interesting subset of our target sample
from the perspective of age analyses.
In the entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of stars are sub-giants,
red giants, and helium-burning red-clump stars.
We failed to obtain light curves for roughly $5\%$ of the stars on silicon, 
primarily due to our masking of saturated stars and their nearby pixels.

Finally, 
Figure~\ref{fig:propermotions} shows the proper motions
of the entire and close samples of stars on silicon.
Each clump signifies a different star cluster. The central
blob in the top figure is in fact two separate blobs,
due to the different directions in the Galaxy being observed
in Sectors 6 and 7.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} 
  Black points correspond to the minimum RMS across the available three
  aperture sizes.  
  The model (orange and gray lines) assumes aperture sizes reported 
  by \citet{Sullivan_et_al_2015}, and the effective area from 
  \citet{vanderspek_2018}.
  The noise from unresolved background stars (dotted gray line) is a function 
  of galactic latitude, and dominates over zodiacal light
  for faint stars near the galactic plane; the line shown assumes a
  sight-line towards the center of Sector 6, Camera 1 (further details
  are in \S~\ref{subsubsec:rmsvsmag}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

\begin{figure}[!t]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}
